--- 
title: "Glossary"
author: "psyTeachR Team"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
description: "Definitions of technical terms"
---

```{r cite-packages, include = FALSE}
# automatically create a bib database for R packages
# add any packages you want to cite here
knitr::write_bib(c(
  .packages(), 'bookdown', 'tidyverse'
), 'packages.bib')

```

# Overview {-} 

If you are using the [psyTeachR book template](](/book-template/), you can use the glossary function to automatically link to a term in the and automatically include a tooltip with a short definition when you hover over the term. Use the following syntax in inline r: `glossary("word")`. For example, common `r glossary("data type", "data types")` are `r glossary("integer")`, `r glossary("double")`, and `r glossary("character")`.

If you need to link to a definition, but are using a different form of the word, add the display version as the second argument (`display`). You can also override the automatic short definition by providing your own in the third argument (`shortdef`). Add the argument `link = FALSE` if you just want the hover definition and not a link to the psyTeachR glossary.

```{r glossary-example, results='asis'}
glossary("data type", 
         display="Data Types", 
         shortdef="My custom definition of data types", 
         link = FALSE)
```

You can add a glossary table to the end of a chapter with the following code. It creates a table of all terms used in that chapter previous to the `glossary_table()` function.

```{r, eval=FALSE, verbatim="r, echo=FALSE, results='asis'"} 
glossary_table()
```

`r glossary_table()`

If you want to contribute to the glossary, fork the [github project](https://github.com/PsyTeachR/glossary), add your terms and submit a pull request, or suggest a new term at the [issues page](https://github.com/PsyTeachR/glossary/issues).


