## atomic

<dfn>Only containing [objects](o.html#object) with the same [data type](d.html#data-type) (e.g., all [numeric](n.html#numeric) or [character](c.html#character)).</dfn>

[Vectors](v.html#vector) are atomic data structures in R.

```{r}
a <- c(1, 4, 32)
b <- c("somebody", "once", "told me")
class(a)
class(b)
```

<details>
  <summary>More...</summary>
  
If you try to mix data types in an atomic vector, they will be [coerced](c.html#coerce) to be the same type. (Note that 32 becomes "32" so it can be in the same vector as a character object).

```{r}
c(32, TRUE, "eighteen")
```

Another feature of vectors that makes them atomic is that they are always flat. If you embed vectors within vectors, they will be flattened.

```{r}
c(7, c(1, 4, 32), 2, 6)
```

[Lists](l.html#list), on the other hand, can be nested.

```{r}
list(7, c(1, 4, 32), 2, 6) %>% str()
```


If you try to extract objects inside an atomic vector, you need to use [brackets](b.html#brackets) `[]`. This can be with an index or a name. Single brackets can return one or more elements, and include names, while double brackets can only return one element and don't have names.

```{r}
my_vec <- c(x = 3, y = 1, z = 4)
my_vec[2]
my_vec["y"]
my_vec[["y"]]
```


You cannot use the $ operator on an atomic vector, or you will get this very common error.

```{r, error = TRUE}
my_vec$y
```

See the [Vectors chapter](https://adv-r.hadley.nz/vectors-chap.html#atomic-vectors) of Advanced R for more advanced discussion of atomic vectors.

</details>
