## brackets

<dfn>Square brackets used to subset a [container](c.html#container) like a [vector](v.html#vector), [list](l.html#list), [data frame](d.html#data-frame), or [matrix](m.html#matrix) (e.g., mtcars[[1]] or mtcars[1:2]).</dfn>

When you use [single brackets](s.html#single-brackets) to subset a container, you get back a container with the items you selected. This contrasts with [double brackets](d.html#double-brackets), which only return a single item in the container.



You can use single brackets to select one or more items from a vector.

```{r}
secret_code <- c(16, 19, 25, 20, 5, 1, 3, 8, 18)

LETTERS[secret_code]
```

If you use double brackets, you can only select a single item from the vector. If you try to select more than one, you will get the following error messge.

```{r, error = TRUE}
LETTERS[[secret_code]]
```



You can select items by [index](i.html#index) or name. `mylist[c("a", "c")]` returns a list containing the first and third items.

```{r}
mylist <- list(
  a = 10,
  b = 20,
  c = 30
)

mylist[c("a", "c")]
```

Single brackets return the same type of container as the [object](o.html#object) being subset, so `mylist[1]` returns a [list](l.html#list) containing just the first item.

```{r}
mylist[1]
```

Double brackets return the same type of object as the single item being selected, so `mylist[[1]]` returns a [vector](v.html#vector) that is the same as the first item in `mylist`.

```{r}
mylist[[1]]
```



Single brackets let you select rows and columns of a [data frame](d.html#data-frame) or [tibble](t.html#tibble), if you separate them by a comma.

```{r}
data <- data.frame(
  id = 1:3,
  letter = c("a", "b", "c"),
  vowel = c(TRUE, FALSE, FALSE)
)

# rows 1:2 and columns 3:4
data[1:2, 2:3]
```

If you omit the rows or columns, you select them all.

```{r}
data[1, ] # row 1, all columns
```

```{r}
data[, 1:2] # all rows, columns 1:2
```

<div class="warning">
If you only select one column of a data frame with single brackets, you will get a vector back instead of a data frame. You can change this behaviour by using `drop = FALSE`.

```{r}
data[, 1] # returns a vector
```
```{r}
data[, 1, drop = FALSE] # returns a data frame
```

[Tibbles](t.html#tibble) always returns a tibble. 

```{r}
as_tibble(data)[, 1] # returns a tibble
```
</div>

Double brackets can be used with a single index or name to select a column as a vector.

```{r}
data[["vowel"]]
```
Or with row and column values to select a single cell.

```{r}
data[[1, "vowel"]]
```
You can't use double brackets to select a single row of a data table.

```{r, error = TRUE}
data[[1, ]]
```

More complex containers like 3-dimensional [arrays](a.html#array) can have more than 2 values in the brackets, but work on the same principles.

```{r}
myarray <- array(1:8, dim = c(2, 2, 2))
myarray[2, 2, 2]
```



