## concatenate

<dfn>To combine strings or vectors.</dfn>

When referring to strings, concatenate means to add strings together using the function `paste` (adds a space between strings) or `paste0` (doesn't add anything between strings). 

```{r concatenate-demo1}
subject_name <- "Lisa"
paste("Hello,", subject_name)
```

When referring to other types of variables, concatenate can mean to create a vector with those variables, usually using the `c` function. For example, you could concatenate the numbers 1, 3, 6, and 10 like this: `c(1, 3, 6, 10)`. You can concatenate two [vector](#vector)s as well:

```{r concatenate-demo2}
v1 <- 1:5
v2 <- 11:15
c(v1, v2)
```

```{block, type="warning"}
Remember, a [vector](#vector) can only have one [data type](#data_type). So if you concatenate a [string](#string) vector and a [numeric](#numeric) vector, the numbers will get turned into their string versions. If you concatenate an [integer](#integer) and a [double](#integer) vector, the integers will be converted to doubles.
```

```{r concatenate-demo3}
strings <- c("a", "c", "e")
integers <- c(1L, 3L, 5L)
doubles <- c(1.1, 3.3, 5.5)
c(strings, integers)
c(doubles, integers)
```
