## default value

<div class="translation" lang="en">

<dfn>A value that a [function](f.html#function) uses for an [argument](a.html#argument) if it is skipped.</dfn>

For example, `mean()` has a default value of `FALSE` for the argument `na.rm` (don't ignore NA values). 

```{r}
x <- c(1,2,3,NA)
mean(x)
```
So if you leave that argument out, it's the same as setting it to `FALSE`.

```{r}
mean(x, na.rm = FALSE)
```

And you have to explicitly set it if you want it to be different.

```{r}
mean(x, na.rm = TRUE)
```

If an argument does not have a default value, you can't omit it. In the example below, there is no default value for `n`.

```{r, error = TRUE}
x = rnorm()
```

</div>

<div class="translation" lang="zh-Hant">

<dfn>TRANSLATED TERM:預設值 任何R[函式](f.html#function)事先設定的[參數](a.html#argument)數值，編寫程式碼未設定即取用的數值。</dfn>

請測試以下程式碼：<br/>
`mean()` 的其中一項參數`na.rm`，預設值是 `FALSE`(表示計算不忽略NA)。 

```{r}
x <- c(1,2,3,NA)
mean(x)
```

即使寫出參數及預設值，計算結果也是一樣。

```{r}
mean(x, na.rm = FALSE)
```

更改參數數值，才會得到不同的結果。

```{r}
mean(x, na.rm = TRUE)
```

如果參數未指定預設值，通常必須手動指定數值。以下例子直接執行會有錯誤，因為參數`n`沒有預設值。
 
```{r, error = TRUE}
x = rnorm()
```
  
</div>
