## dimension

<dfn>An axis used to locate or specify a data point in a data structure (e.g., vectors have 1 dimension and data frames have 2: rows and columns)</dfn>

For example, [vectors](v.html#vector) are 1-dimensional, so you only need one [index](i.html#index) to specify a value. [Data frames](d.html#data-frame) and [matrices](m.html#matrix) are 2-dimensional, so need two numbers to specify a value. [Arrays](a.html#array) can have any number of dimensions.

Dimension can also refer to the number of elements in each dimension that an object has, which you can determine with the `dim()` function (or the `length()` function for vectors).

<details>
  <summary>More...</summary>
  
The code below arranges the numbers 1 to 12 in data structures with 1, 2 or 3 dimensions and shows how to [extract](e.html#extract-operator) the value 3 from each.

```{r}
# 1-dimensional vector
v <- 1:12
v
length(v)
v[3] # index
```


```{r}
# 2-dimensional data frame
df <- data.frame(
  a = 1:6,
  b = 7:12
)
df
dim(df)
df[3, 1] # row, column
```


```{r}
# 2-dimensional matrix
m <- matrix(1:12, nrow = 2)
m
dim(m)
m[1, 2] # row, column
```


```{r}
# 3-dimensional array
a <- array(1:12, dim = c(2, 3, 2))
a
dim(a)
a[1, 2, 1] # row, column, D3
```

</details>

