## estimated marginal means

<dfn>The means for cells in a design, as estimated from a statistical model, rather than from data</dfn>

Also known as least-squares means.

<details>
  <summary>More...</summary>

Here we simulate some data for a 2x2 [factorial](f.htmlfactorial-stats) design. The argument `mu` specifies the cell means for ctl-A, ctl-B, exp-A and exp-B.

```{r}
# simulate some factorial data
set.seed(8675309)
simdat <- faux::sim_design(
  between = list(
    treatment = c("ctl", "exp"),
    group = c("A", "B")
  ),
  mu = c(100, 100, 105, 110),
  sd = 10
)
```

Then we model the data using a [linear model])g.html#general-linear-model).

```{r}
# model using lm
model <- lm(y ~ treatment * group, data = simdat)
summary(model)
```

Use the `emmeans` package to get the estimated marginal means from this model. You can get the estimated means for each combination of treatment and group:

```{r}
emmeans::emmeans(model, ~ treatment | group)
```

Or for the main effects separately (there will be a warning that the interaction may make this misleading).

```{r}
emmeans::emmeans(model, ~ treatment)
```

```{r}
emmeans::emmeans(model, ~ group)
```

</details>
