## factorial

<dfn>[factorial](f.html#factorial-stats)): Experimental designs where all possible combinations of [independent variables](i.html#independent-variable) are considered; [factorial](f.html#factorial-math)): The mathematical operation where an integer is multiplied by every integer between 1 and itself</dfn>

## factorial (stats) {#factorial-stats}

<dfn>Experimental designs where all possible combinations of [independent variables](i.html#independent-variable) are considered.</dfn>

For example, the following design has two factors: time and treatment, and all 4 combinations are represented in the data.

```{r, echo = FALSE}
# simulate some factorial data
set.seed(8675309)
simdat <- faux::sim_design(
  n = 100,
  within = list(time = c("pre", "post")),
  between = list(treatment = c("control", "experimental")),
  mu = c(100, 100, 100, 105),
  sd = 10,
  r = 0.5,
  id = "ID",
  dv = "DV",
  long = TRUE
)
```

## factorial (math) {#factorial-math}

<dfn>The mathematical operation where an integer is multiplied by every integer between 1 and itself.</dfn>

This operation is represented by an exclamation point in mathematical notation (e.g., `5!`) and uses the `factorial()` function in R.

```{r}
# 5 factorial
factorial(5)
5 * 4 * 3 * 2 * 1
```


