## factor

<dfn>A data type where a specific set of values are stored with labels; An explanatory variable manipulated by the experimenter</dfn>

## factor (data type) {#factor-data-type}

<dfn>A data type where a specific set of values are stored with labels</dfn>

In tables, you can store strings as [characters](c.html#character) or factors.

```{r factor}
data <- tibble(
  chr = c("A", "B", "C"),
  fctr = factor(c("A", "B", "C"))
)
```

If you print a character [vector](v.html#vector), it will have quotes around each values, while a factor vector will show the [Levels](l.html#level) after.

```{r factor-vector}
data$chr

data$fctr
```

In a [tibble](t.html#tibble), these types will have "<chr>" or "<fctr>" under the column header. 

```{r factor-tibble}
data
```

You can convert between characters and factors like this:

```{r factor-convert}
as.character(data$fctr)

# set the levels to the order you want
factor(data$chr, levels = c("C", "B", "A"))
```


### Resources

* [Factors](https://r4ds.had.co.nz/factors.html) in R for Data Science



## factor (experimental) {#factor-experimental}

<dfn>An explanatory variable manipulated by the experimenter</dfn>

For example, imagine an experiment where you test half of subjects in a dark room with easy, medium, and hard tasks, and the other half in a light room with easy and hard tasks. This experiment has two **factors**: room darkness and task difficulty. The factor of room darkness is [between subjects](b.html#between-subjects) and has two [levels](l.html#level): dark and light. The factor of task difficulty is [within subjects](w.html#within-subjects) has three levels: easy, medium, and hard.

See [independent variable](i.html#independent-variable)


