## iteration

<dfn>Repeating a process or function</dfn>

Repeating a process or function is useful when we want to perform the same operation on each element in a list or vector.

For example, you may want to check the power of a two-sample t-test to detect an effect size of 0.2 for all of the possible sample sizes between 100 and 1000, incrementing by 100. You can "iterate" over the values of n to get the power for each n.

```{r}
n_range <- seq(100, 1000, 100)
power <- c() # make an empty vector

for (n in n_range) {
  pcalc <- power.t.test(n = n, delta = 0.2, sd = 1, 
                      type = "two.sample")
  power <- c(power, pcalc$power)
}

power
```

Many functions are "vectorized" such that they return a vector of results if you use a vector for an argument. The function itself takes care of the iteration for you.

```{r}
pcalc <- power.t.test(n = n_range, 
                      delta = 0.2, sd = 1, 
                      type = "two.sample")
power <-  pcalc$power
power
```

You can also use `apply()` or `map()` functions to apply a single function to each element of a vector or list. 

```{r}
# apply power.t.test to each n and return a list of lists
pcalc <- map(.x = n_range, # vector to iterate over
             .f = power.t.test, # function to apply
             # other arguments to the function
             delta = 0.2, sd = 1, 
             type="two.sample")

# extract the "power" element from each element in pcalc
# and return a vector of doubles
power <- map_dbl(pcalc, getElement, "power")
power
```


