## library

<dfn>The [function used to load packages](l.html#library-function) or the [directory where packages are stored](l.html#library-directory).</dfn>


## library (function) {#library-function}

<dfn>The function used to load packages.</dfn>

You can use the `library()` function to load [packages](p.html#package). This makes the functions in the package available to use without prefixing them with the package name.

If you try to use a non-prefixed function without loading its package, you will get an error like this:

```{r, include = FALSE}
# make sure glue isn't loaded
library(glue)
detach("package:glue")
```


```{r, error = TRUE}
glue("My name is {name}", name = "Lisa")
```


You can use this function with its package prefix (helpfully, the `glue()` function comes from the glue package).

```{r}
glue::glue("My name is {name}", name = "Lisa")
```

Or you can load the package with `library()` and use it without the prefix.

```{r, message=FALSE}
library(glue)

glue("My name is {name}", name = "Lisa")
```

## library (directory) {#library-directory}

<dfn>The [directory](d.html#directory) where [packages](p.html#package) are stored.</dfn>

Find out the location(s) where your packages are stored with the following code:

```{r}
.libPaths()
```

If you have problems installing packages, you may need to change your library location to a directory that you have permission to write to. You can do this by setting the library path.

```{r, eval = FALSE}
# use a path relevant to your computer
.libPaths("/Users/myaccount/R/Library")
```

