## NA

<dfn>A missing value that is "Not Available"</dfn>

You can use `NA` to represent missing values in a [vector](v.html#vector). Use the function `is.na()` to check if values are missing.

```{r na-ex-1}
values <- c(1,4,NA,3,4)
is.na(values)
```

If the results of a calculation like `mean()` or `sd()` is `NA`, this usually means that you have some missing values in your vector. You can remove `NA` values using `na.rm = TRUE` in many functions.

```{r na-rm}
mean(values)
mean(values, na.rm = TRUE)
```

Dealing with missing values when calculating correlations is a little trickier.

```{r na-cor}
dat <- tribble(
  ~x, ~y, ~z,
   1,  3, NA, # x-y included when p.c.o
   2,  1,  4, 
   3,  5,  3,
   4,  1,  2,
  NA,  5,  1  # y-z included when p.c.o
)


# uses only rows 2:4 for all correlations
cor(dat, use = "complete.obs")

# uses rows 1:4 for x-y, 2:5 for y-z, and 2:4 for x-z
cor(dat, use = "pairwise.complete.obs")
```
You can filter a table down to only rows with no NA values using `na.omit()`.

```{r}
complete_dat <- na.omit(dat)
```

`r kable(na.omit(dat))`





