## partial eta squared

<dfn>A measure of effect size commonly used in [ANOVAs](a.html#anova)</dfn>

It measures the proportion of [variance](v.html#variance) explained by a specific [independent variable](i.html#independent-variable) after accounting for variance explained by other variables in the model. It can range from 0 (explains no variance) to 1 (explains 100% of the variance).

The formula for partial eta squared is:

$\eta_p^2 = SS_{effect} / (SS_{effect} + SS_{error})$


* $SS_{effect}$: The sum of squares of for the target effect
* $SS_{error}$: The sum of squares error in the ANOVA

<details>
  <summary>More...</summary>

In the example below, we'll simulate data with significant main effects and an interaction.

```{r}
# simulate some factorial data
set.seed(8675309)
simdat <- faux::sim_design(
  n = 100,
  within = list(time = c("pre", "post")),
  between = list(treatment = c("control", "experimental")),
  mu = c(100, 105, 100, 110),
  sd = 10,
  r = 0.5,
  id = "ID",
  dv = "DV",
  long = TRUE
)
```

The afex package defaults to generalised eta squared, so you have to set the reported effect size to "pes" to get partial eta squared.

```{r}
# analysis with ANOVA

library(afex) # a useful package for anova

# set effect size measure to partial eta squared
afex::afex_options(es_aov = "pes")

anova <- afex::aov_ez(
  id = "ID",
  dv = "DV",
  between = "treatment",
  within = "time",
  data = simdat
)

afex::nice(anova)
```

</details>
