## pipe

<dfn></dfn>

Pipes are a way to order your code in a more readable format.

The symbol `%>%` takes the [object](o.html#object) created by a function and sends it to the next function. By default, it will be used as the first [argument](a.html#argument), and most [tidyverse](t.html#tidyverse) functions are optimised for this, but you can also include the result as another argument using `.` (see the example below).


Instead of making a new object for each step:

```{r, include = FALSE}
set.seed(1)
```

```{r}
# this makes 4 unnecessary objects
data <- rnorm(20)         # simulate 20 values
t <- t.test(data)         # 1-sample t-test
p <- t$p.value            # extract p-value
rounded_p <- round(p, 3)  # round to 3 digits
paste("p = ", rounded_p)  # format
```

Or nesting functions:

```{r, include = FALSE}
set.seed(1)
```

```{r}
# this is unreadable; never do this
paste("p = ", round(t.test(rnorm(20))$p.value, 3))
```

You can pipe the results of each function to the next function:

```{r, include = FALSE}
set.seed(1)
```


```{r}
rnorm(20) %>%         # simulate 20 values
  t.test() %>%        # 1-sample t-test
  `[[`("p.value") %>% # extract p-value, `[[`(data, "x") is the same as data[["x"]]
  round(3) %>%        # round to 3 digits
  paste("p = ", .)    # format 
                      # use . to represent the previous data if it's not the first argument
```


See a more [detailed example](https://debruine.github.io/posts/pipes/){target="_blank"}. 


The [symbol](symbols.html) `|` is also called a "pipe" and means "OR" in R, although it has other meanings that are more similar to the `%>%` pipe in some other programming languages.


