## Q-Q plot

<dfn>A scatterplot created by plotting two sets of [quantiles](q.html#quantile) against each other, used to check if data come from a specified [distribution](d.html#distribution)</dfn>

```{r, echo = FALSE}
set.seed(8675309)
```


It is pretty difficult to tell from looking at a density plot if data are distributed in a specific way. We often want to determine if, for example, the residuals of a model are normally distributed. Q-Q plots can help with this.

Let's simulate 25 data points from a normal distribution with a mean of 100 and SD of 10. Since there are not many data points, the resulting plot will be pretty lumpy. The red line is a perfect normal distribution.

```{r qq-density, fig.cap = "Density plot of sample data and the normal distribution it was drawn from"}
A <- rnorm(25, 100, 10)

ggplot() + 
  geom_density(aes(A)) +
  geom_function(fun = dnorm, 
                args = list(mean = 100, sd = 10),
                colour = "red")
```

A Q-Q plot calculates what [quantile](q.html#quantile) each data point is in, and plots that against the theoretical quantiles from the normal distribution. The red line is the theoretically perfect noraml distribution, so you just need to assess if most of the points fall on this line.

```{r qq-A, fig.cap = "Q-Q plot of a small sample from a normal distribution"}
qplot(sample = A) + geom_qq_line(colour = "red")
```

Here's what it might look like if your data are actually from a uniform distribution. 

```{r qq-unif, fig.cap = "Q-Q plot of a uniform distribution"}
U <- runif(25, 0, 10)
qplot(sample = U) + geom_qq_line(colour = "red")
```
