## reprex

<dfn>A reproducible example that is the smallest, completely self-contained example of your problem or question.</dfn>

For example, you may have a question about how to figure out how to select rows that contain the value "test" in a certain column, but it isn't working. It's clearer if you can provide a concrete example, but you don't want to have to type out the whole table you're using or all the code that got you to this point in your script. 

You can include a very small table with just the basics or a smaller version of your problem. Make comments at each step about what you expect and what you actually got. 

Which version is easier for you to figure out the solution?

```{r, eval = FALSE}
# this doesn't work
no_test_data <- data %>%
  filter(!str_detect(type, "test"))
```


```{r, eval = FALSE}
# with a minimal example table
data <- tribble(
  ~id, ~type, ~x,
  1, "test", 12,
  2, "testosterone", 15,
  3, "estrogen", 10
)

# this should keep IDs 2 and 3, but removes ID 2
no_test_data <- data %>%
  filter(!str_detect(type, "test"))
```

One of the big benefits to creating a reprex is that you often solve your own problem while you're trying to break it down to explain to someone else.

If you really want to go down the rabbit hole, you can create a reproducible example using the [reprex](https://www.tidyverse.org/help/#reprex) package from tidyverse.

