## residual

<dfn>Defined as the deviation of an observation from a model's expected value.</dfn>

Mathematically, the residual is defined as the observed value minus the model's [fitted value](f.html#fitted-value) for that observation.

For example, the linear model $\hat{Y_i} = 3 + 2 X_i$ predicts a value of $\hat{Y}_i = 7$ for $X_i = 2$. If you happen to have observed $Y_i = 8$ for observation $i$, then the residual for that observation would be $Y_i - \hat{Y}_i = 8 - 7 = 1$.

A related but slightly different notion is [error](e.html#error).

For example, below we simulate data for two groups of 50 with means of 100 and 105 (and SDs of 10). 

```{r}
set.seed(8675309) # for reproducibility

group0 <- rnorm(n = 50, mean = 100, sd = 10)
group1 <- rnorm(n = 50, mean = 105, sd = 10)

df <- data.frame(
  dv = c(group0, group1),
  group = rep(0:1, each = 50)
)

model <- lm(dv ~ group, data = df)

summary(model)

model$coefficients
```

The model above has an intercept of `r round(model$coefficients[[1]], 1)` and an effect of group of `r round(model$coefficients[[2]], 1)`, meaning that the predicted value for group 0 is `r round(model$coefficients[[1]], 1)` and the predicted value for group 1 is `r round(model$coefficients[[1]] + model$coefficients[[2]], 1)`. The difference between these predictions and the observed values is the [residual](r.html#residual) error.


```{r}
intercept <- model$coefficients[[1]]
effect <- model$coefficients[[2]]

df |>
  mutate(predicted = intercept + effect * group,
         residual = dv - predicted) |>
  group_by(group) |>
  slice(1:5) # show 5 from each group
```
