## standardize

<dfn> The process of putting [vectors](v.html#vector) on the same scale. In statistics, this often means that a vector has a [mean](m.html#mean) of 0 and a [standard deviation](s.html#standard-deviation) of 1. </dfn>

You can standardize a vector by subtracting the vector mean from each value 
and then dividing each each difference by the vector standard deviation, or by using the `scale()` function.

<details>
  <summary>More...</summary>

Standardize a vector manually:

```{r}
# create a vector containing the numbers 1 to 10
v <- 1:10

# calculate mean and SD
v_mean <- mean(v)
v_sd <- sd(v)

# standardize
standardized_v <- (v - v_mean) / v_sd

data.frame(
  original = v,
  standardized = standardized_v
)
```

Now the mean and standard deviation of the new vector will be 0 and 1

```{r}
mean(standardized_v)
sd(standardized_v)
```

You can also use the scale() function in R to automate the standardization process.

```{r}
scaled_v <- scale(v)

mean(scaled_v)
sd(scaled_v)
```

::: {.warn}

The result of the `scale()` function is a 2-[dimensional](d.html#dimension) [matrix](m.html#matrix), so you usually need to extract the vector of values like this:

```{r}
scaled_v[, 1]
```

:::

</details>