## vector

<dfn>A type of data structure that collects values with the same [data type](d.html#data-type), like T/F values, numbers, or strings.</dfn> 

The following things are examples of vectors:

```{r vector-demo1}
# use the c() function to make a vector of strings or numbers
ingredients <- c("vodka", "gin", "rum", "tequila", "triple sec", 
                      "orange juice", "coke", "sour mix")

fun_to_play_at <- c(25, 13, 3, 1)

# the colon between two integers gives you all the numbers from the first to the last integer
likert <- 1:7
```

<details>
  <summary>More...</summary>

[Elements](e.html#element) are always the same data type. If you try to combine values with different data types, they are [coerced](c.html#coercion) into a common data type. Use a [list](l.html#list) to combine values with different types without coercion.

The variable `letters` is a built-in vector with the Latin letters in order. You can select part of a vector by putting the numeric location (or [index](i.html#index)) of what [element](e.html#element) you want inside of square brackets after the vector. You can even put a vector of numbers inside the square [brackets](b.html#brackets) to select several elements.

```{r vector-demo2}
letters[26]
letters[1:5]
letters[fun_to_play_at]
```


See [Ch 20 of R for Data Science](http://r4ds.had.co.nz/vectors.html){target="_blank"} for a thorough explanation of vectors.

</details>
