## vector

<dfn>A type of data structure that is basically a list of things like T/F values, numbers, or strings.</dfn> 

It can get very complicated (see [Ch 20 of R for Data Science](http://r4ds.had.co.nz/vectors.html) for a thorough explanation), but at first you just need to be able to understand that the following things are examples of vectors:

```{r vector-demo1}
# use the c() function to make a vector of strings or numbers
liit_ingredients <- c("vodka", "gin", "rum", "tequila", "triple sec", 
                      "orange juice", "coke", "sour mix")

fun_to_play_at <- c(25, 13, 3, 1)

# the colon between two integers gives you all the numbers from the first to the last integer
likert <- 1:7
```

The variable `letters` is a built-in vector with the latin letters in order. You can select part of a vector by putting the numeric location (or [index](#index)) of what [element](#element) you want inside of square brackets after the vector. You can even put a vector of numbers inside the square brackets to select several elements.

```{r vector-demo2}
letters[26]
letters[1:5]
letters[fun_to_play_at]
```